---
title: "Milestone Report - Capstone Project"
author: "M Poobalan"
date: "March 18, 2016"
output:
  html_document:
    highlight: tango
    toc: yes
    toc_depth: 3
---
#Introduction

This document presents the analysis of datasets for text prediction models, and provide the roadmap for the proposed text prediction models.


Data for this project is obtained from SwiftKey (see Reference below for link) and contains 3 types of textual data - from **Twitter**, **blogs** and **news**, each available in four languages. For the purpose of this project, data for **English** language is used.

eval to run or not
echo to display code or not
results to hide or show code results
message
warning 
cache for caching



#Loading Data
```{r loading, cache=TRUE, warning=FALSE}
datatwitter <-readLines(conn <-file("./data/en_US.twitter.txt",encoding="UTF-8"))
close(conn)
datablog <- readLines(conn <-file("./data/en_US.blogs.txt",encoding="UTF-8"))
close(conn)
datanews <- readLines(conn <-file("./data/en_US.news.txt","rb",encoding="UTF-8"))
close(conn)
```



#Data Exploration
The file size, object size (in memory) and number of lines in each dataset is quite big as shown below:

```{r basicinfo, warning=FALSE, echo=FALSE, results='hide'}
#calc file size
file.info("./data/en_US.twitter.txt")$size/1024/1000
file.info("./data/en_US.blogs.txt")$size/1024/1000
file.info("./data/en_US.news.txt")$size/1024/1000

twtinfo <- c(format(file.info("./data/en_US.twitter.txt")$size/1024/1000,digits=6),format(object.size(datatwitter),units="auto"),prettyNum(length(datatwitter),big.mark = ",",width=7))
bloginfo <- c(format(file.info("./data/en_US.blogs.txt")$size/1024/1000,digits=6),format(object.size(datablog),units="auto"),prettyNum(length(datablog),big.mark = ",",width=8))
newsinfo <- c(format(file.info("./data/en_US.news.txt")$size/1024/1000,digits=6),format(object.size(datanews),units="auto"),prettyNum(length(datanews),big.mark = ",",width=7))

datainfo <- rbind(twtinfo, bloginfo,newsinfo)

rownames(datainfo) <- c("Twitter", "Blogs", "News")
colnames(datainfo) <- c("File Size (MB)", "Object Size", "Lines")
```

```{r showinfo}
library(knitr)

knitr::kable(datainfo)
```


#Cleaning Data


#Creating Sample

#Creating Corpus

#n-gram

#Way Forward

#References

1. Data source from SwiftKey - [download zip file](<https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip)
2. Dataset Corpus (HC Corpora) - [Read me file](http://www.corpora.heliohost.org/aboutcorpus.html)
3. Blacklisted words
4. 

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
